Clearance Project - 1 - Data Generation

### 2025-03-19 data-raw/ClearanceProject-1-DataRmd.Rmd
Updated parameter collating functions to use chemical DTXSIDs and merges to maintain correct order.

chem_properties <- get_chem_info_batch(
  DTXSID = chem_info$dtxsid,
  type = '', 
  rate_limit = 0L,
  verbose = TRUE
) 
# This takes a minute or so... save a reference RDS file to load
# Also get rid of any that don't have SMILES
chem_info %>% distinct(dtxsid, preferredName,
                              qsarReadySmiles, monoisotopicMass) %>%
  right_join(chem_properties) %>%
  filter(!is.na(qsarReadySmiles)) %>%
  saveRDS(file = "data-raw/ctxR_3comp2_cheminfo.rds")

@@

rpr_clint_df <- data.frame(Chemical = names(rpr_param_rest_l),
                           CLint = vapply(names(rpr_param_rest_l),
                                          \(x) {
                                            rpr_param_rest_l[[x]][["Clint"]]
                                          },
                                          FUN.VALUE = numeric(1L)
                           ))

save(rpr_param_rest_l, rpr_param_nrest_l,
     rpr_param_df, rpr_httk_clearance_df,
     rpr_httk_preds, rpr_css_df, rpr_clint_df,
     file = "data-raw/rat_pars_rat.RData")
```

@@

save(rph_param_rest_l, rph_param_nrest_l,
     rph_param_df, rph_httk_clearance_df,
     rph_httk_preds, rph_css_df, rph_clint_df,
     file = "data-raw/rat_pars_human.RData")
```

>>>>

chem_properties <- get_chem_info_batch(
  DTXSID = chem_info$dtxsid,
  type = '', 
  rate_limit = 0L,
  verbose = TRUE
) 
# This takes a minute or so... save a reference RDS file to load
# Also get rid of any that don't have SMILES
chem_info %>% distinct(dtxsid, preferredName,
                              qsarReadySmiles, monoisotopicMass) %>%
  right_join(chem_properties) %>%
  filter(!is.na(qsarReadySmiles)) %>%
  saveRDS(file = "data-raw/RCdata/ctxR_3comp2_cheminfo.rds")

@@

rpr_clint_df <- data.frame(Chemical = names(rpr_param_rest_l),
                           CLint = vapply(names(rpr_param_rest_l),
                                          \(x) {
                                            rpr_param_rest_l[[x]][["Clint"]]
                                          },
                                          FUN.VALUE = numeric(1L)
                           ))
rownames(rpr_clint_df) <- NULL
rpr_param_df <- merge(rpr_param_df, rpr_clint_df)
rpr_httk_clearance_df <- merge(rpr_httk_clearance_df, rpr_css_df)

save(rpr_param_rest_l, rpr_param_nrest_l,
     rpr_param_df, rpr_httk_clearance_df,
     rpr_httk_preds, file = "data-raw/RCdata/rat_pars_rat.RData")
```

@@

rownames(rph_clint_df) <- NULL
rph_param_df <- merge(rph_param_df, rph_clint_df)
rph_httk_clearance_df <- merge(rph_httk_clearance_df, rph_css_df)

save(rph_param_rest_l, rph_param_nrest_l,
     rph_param_df, rph_httk_clearance_df,
     rph_httk_preds,
     file = "data-raw/RCdata/rat_pars_human.RData")
```
